\documentclass[11pt]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{setspace}
\usepackage{hyperref}

\title{Participant Consent Form for AI-Powered and Traditional MMSE Tool Testing}
\date{}
\pagenumbering{gobble}

\begin{document}

\maketitle
\begin{center}
    \large
    \textbf{Participant Consent Form}
\end{center}
\vspace{0.5cm}

\noindent
You are invited to participate in a research study to evaluate both the AI-powered MMSE tool and traditional paper-based MMSE tests. The purpose of this study is to assess the usability, accuracy, and effectiveness of the AI-powered tool in comparison to traditional methods of cognitive assessment. Your participation will involve completing a series of cognitive assessments using both the AI-powered MMSE tool and traditional paper-based MMSE tests.

\vspace{0.5cm}

\noindent
\textbf{Confidentiality and Data Protection}
\begin{itemize}
    \item Your participation in this study is voluntary, and you may withdraw at any time without penalty.
    \item All data collected during the study will be kept confidential and anonymized.
    \item The data will be used solely for the purposes of this research and will be removed from our records after the analysis is complete.
    \item Your identity will not be revealed in any reports or publications resulting from this study.
\end{itemize}

\vspace{0.5cm}

\noindent
\textbf{Consent}
\begin{itemize}
    \item I understand the purpose of this study and what is expected of me as a participant.
    \item I understand that my participation is voluntary and that I may withdraw at any time without penalty.
    \item I understand that my data will be kept confidential and will be removed after the analysis is complete.
    \item I understand that I will be completing both AI-powered and traditional paper-based MMSE tests.
    \item I agree to participate in this study.
\end{itemize}

\vspace{0.5cm}

\noindent
\textbf{Participant's Signature:} \underline{\hspace{6cm}}

\noindent
\textbf{Participant's Printed Name:} \underline{\hspace{6cm}}

\noindent
\textbf{Date:} \underline{\hspace{6cm}}

\vspace{0.5cm}

\noindent
\textbf{Researcher’s Contact Information}

\noindent
If you have any questions or concerns about this study, please contact:

\begin{tabbing}
\hspace{3cm} \= Name: \hspace{1cm} \= Konstantin Tenman \\
\> Email: \> konstantin@tenman.ee \\
\> Phone: \> +372 511 1618
\end{tabbing}

\end{document}
