\appendix

\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}

\newcounter{appendixcounter}
\renewcommand{\theappendixcounter}{\Roman{appendixcounter}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\refstepcounter{appendixcounter}

\subsection*{\Roman{appendixcounter}. Repository} \label{appendix:repository}

\addcontentsline{toc}{subsection}{I. Repository}

The source code, documentation, and other materials produced for this thesis are available in the following repositories:
\begin{itemize}
    \item Master's Thesis: \url{https://github.com/ktenman/master-thesis-ut}
    \item MMSE Prototype App: \url{https://github.com/ktenman/mmse-app}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\licencehint}[2]{\\\hspace*{#1}\textsl(#2)\par}

\refstepcounter{appendixcounter}

\subsection*{\Roman{appendixcounter}. Licence}

\addcontentsline{toc}{subsection}{II. Licence}

\subsubsection*{Non-exclusive licence to reproduce thesis and make thesis public}

I, \textbf{\author}, %author's name
%   \licencehint{10mm}{author's name}

\begin{enumerate}
\item
herewith grant the University of Tartu a free permit (non-exclusive licence) to
reproduce, for the purpose of preservation, including for adding to the DSpace digital archives until the expiry of the term of copyright,
\par
\textbf{\thesistitle}, %
%   \licencehint{10mm}{title of thesis}
\par
supervised by \supervisor. %supervisor's name
%   \licencehint{10mm}{supervisor's name}
\item
I grant the University of Tartu a permit to make the work specified in p. 1 available to the public via the web environment of the University of Tartu, including via the DSpace digital archives, under the Creative Commons licence CC BY NC ND 3.0, which allows, by giving appropriate credit to the author, to reproduce, distribute the work and communicate it to the public, and prohibits the creation of derivative works and any commercial use of the work until the expiry of the term of copyright.
\item
I am aware of the fact that the author retains the rights specified in p. 1 and 2.
\item
I certify that granting the non-exclusive licence does not infringe other persons' intellectual property rights or rights arising from the personal data protection legislation. 
\end{enumerate}

\noindent
Konstantin Tenman\\ %author's name
\textbf{\textsl{13/08/2024}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\refstepcounter{appendixcounter}

\subsection*{\Roman{appendixcounter}. Writing Workflow} \label{appendix:writing-workflow}

\addcontentsline{toc}{subsection}{III. Writing Workflow}

The writing and building of this work exploited quite a wide range of tools, extensions, and environments. This appendix documents the workflow and tools employed to produce this thesis.

The bedrock of the writing environment was, obviously, \LaTeX{}, a complete document preparation system that allows an author not to worry so much about the formatting but to focus on the content. The primary development environment for TeXing and creating the content of this thesis was Visual Studio Code. The LaTeX Workshop plugin added a fully inclusive feature pack to this versatile, extensible editor with syntax highlighting, code completion, real-time compilation, and dynamic preview. Overleaf is an online \LaTeX{} editor used due to its collaboration and template management features.

Version control was done with Git, using GitHub as a host for the remote repository. This repository contains the \LaTeX{} source files, the MMSE prototype app code, and the relevant documentation. It follows this in Appendix~\ref{appendix:repository}. Through Visual Studio Code, plugins like Code Spell Checker and LTeX LanguageTool aided real-time spelling and grammar checks. GitHub Copilot was integrated to complete the code and debug the prototype app.

Beyond the core development environment, AI tools such as ChatGPT, Claude AI, Gemini Pro, and others significantly summarized, rewrote, contextualized, and perfected the different content sections. AI Assistants also helped generate code snippets and explain awkward command-line interfaces. Grammarly provided fine-grained language finesse. Diagramming tools have been utilized to create figures and diagrams that include images and icons from trusted web sources.